Weather anomalies associated with wildfires in the Great Plains

### 2021-05-10 data/PrelimAnalysis/SecondaryAnalysis.Rmd
update

---
title: Weather anomalies associated with wildfires in the Great Plains
subtitle: Preliminary analysis
date: '`r Sys.Date()`'
author: DAM
output:
  html_document:
    keep_md: false
    toc: true
    toc_float: true
    theme: united
    highlight: tango
---

@@

pacman::p_load(tidyverse, sf, lubridate, grid)
options(dplyr.summarise.inform = FALSE)
source('https://raw.githubusercontent.com/devanmcg/rangeR/master/R/CustomGGplotThemes.R')
```

```{r data_loading}
wd =  "C:/Users/devan.mcgranahan/GithubProjects/GreatPlainsFire"
# GIS layers
  load(paste0(wd, './gis/Robjects/us_sf.Rdata'))
  load(paste0(wd, '/gis/Robjects/gp_l3.Rdata'))
  load(paste0(wd, '/gis/Robjects/GP_WF.Rdata'))
  load("C:/Users/devan.mcgranahan/GithubProjects/FireWeather/mapping/data/region_states.Rdata")

# weather data 
  load(paste0(wd, '/data/HistoricalWeather/NWGP_top_20.Rdata'))
  load(paste0(wd, '/data/PrelimAnalysis/FireWeekMeans.Rdata'))
  load(paste0(wd, '/data/PrelimAnalysis/FireEventWx.Rdata'))
```

@@

```{r incident_map}
fires <- 
  NWGP_top_20 %>%
  group_by(incident) %>%
  slice(1) %>%
  st_as_sf(coords = c("lon", "lat"), 
           crs = 4326) %>%
    st_transform(26915)

inset_gg <-
  ggplot() + theme_map(14) +
    geom_sf(data = us_sf, 
            fill = "lightgrey") + 
    geom_sf(data = gp_l3,
            fill = "darkblue", color = NA) + 
    geom_sf(data = gp_l3 %>%
                    filter(US_L3NAME == "Northwestern Great Plains"), 
            fill = "lightblue")

main_gg <-
  ggplot() + theme_map(14) +
    geom_sf(data = gp_l3 %>%
                    filter(US_L3NAME == "Northwestern Great Plains"), 
            fill = "lightblue") + 
    geom_sf(data = region_states, fill = NA) +
    geom_sf(data = fires, 
            pch=21, 
            size = 4, stroke = 1.25,
            fill = "darkblue", 
            color = 'white')

grid.newpage() 
main <- viewport(width = 1, height = 1, x = 0.5, y = 0.5) 
inset <- viewport(width = 0.5, height = 0.5, x = 0.2, y = 0.25)
print(main_gg, vp = main)
print(inset_gg, vp = inset)
# dev.off() 
```

>>>>

---
title: Weather anomalies associated with wildfires in the Great Plains
subtitle: Preliminary analysis with all events in MTBS database
date: '`r Sys.Date()`'
author: DAM
output:
  html_document:
    keep_md: false
    toc: true
    toc_float: true
    theme: united
    highlight: tango
---

@@

pacman::p_load(tidyverse, sf, lubridate, grid, wesanderson)
options(dplyr.summarise.inform = FALSE)
source('https://raw.githubusercontent.com/devanmcg/rangeR/master/R/CustomGGplotThemes.R')
```

```{r data_loading}
wd =  "C:/Users/devan.mcgranahan/GithubProjects/GreatPlainsFire"
# GIS layers
  load(paste0(wd, '/gis/Robjects/mapping.Rdata'))

# Historical weather data for events
  load(paste0(wd, '/data/HistoricalWeather/HistWx.Rdata'))
  load(paste0(wd, '/data/HistoricalWeather/DayOfWx.Rdata'))
```

@@

```{r map}
ggplot() + theme_map(14) +
  geom_sf(data = mapping$us, 
          fill = "grey90") + 
  geom_sf(data = mapping$gp_er, 
          aes(fill = L2))  + 
  geom_sf(data = mapping$gp_st, 
          fill = NA, 
          color = 'grey50') +
  scale_fill_manual(name = 'Level 2 ecoregion',
                    values = wes_palette("Zissou1")) 
```
